|

### 2020-07-11 documents/ovando-et-al-pop-effects-of-mpas.Rmd
finally updated tables to be correct enough for WORD

* fix that mentino of inside and outside stocks

* make clearer the idea that size of parallel trends violation exceeds effect size of MPA

@@

The simulation model consists of 50 patches with wrapped edges. For any one simulation we randomly pull a species and its associated life history traits from the `FishLife` [@thorson2017c] package. We pair these data with randomly selected values governing the characteristics of the simulation (Table.1). These include parameters governing recruitment (variation, autocorrelation, and timing), movement (magnitude of larval and adult dispersal and density dependent movement), fleet dynamics (degree of fishing pressure, distribution of fishing effort), and MPA design (size and placement, habitat characteristics, larval source). The population begins at unfished equilibrium. After fishing effort is applied, each simulation is run to equilibrium with and without the selected MPA design (holding all else constant). In each time step, we measure the difference in biomass densities between the scenario with and without the MPAs to calculate the population effect of the MPAs over time. Simulation results provide a library of plausible MPA effects for a range of biological and economic assumptions.

@@

where $d_i$ is the biomass density at observation *i*, *T* indicates whether the observation *i* is for a targeted ($T = 1$) or non-targeted ($T = 0$) species, and *MPA* marks whether observation *i* is in a pre MPA ($MPA = 0$) or post MPA ($MPA = 1$) state. **B^c^** is a vector of coefficients for additional control variables in matrix *X* such as water visibility and observer experience. **B^s^** is a vector of hierarchical coefficients for each sampling location **S** , clustered by island.  Under the assumptions of this model, $\beta_3$ is the causal effect of the treatment (*MPA*) on the treated (targeted species). $\beta_0$ is the mean total biomass of non-targeted species pre-MPA, and $\beta_1T$ is the mean total biomass of targeted species pre-MPA. $\beta_2MPA$ is the effect of the post-MPA period on the non-targeted species. The shape and scale parameters of the Gamma distribution are estimated as well. Regression details and diagnostic plots are available in the online appendix. The full table of covariates and their posterior means and 89% credible interval can be found in Table.\@ref(tab:did-coefs).

@@

I need to clean these up

Table.2 - Range of simulated variables

| Variable | Distribution|
|---------:|:-----------:|
| Scientific Name | Drawn from all possible species in `FishLife` (@thorson2017c)|
|steepness (h) | ~uniform(0.6,0.95)|
|Adult movement ($\sigma_{s=a}$) | ~uniform(0,0.25 * P)|
|Larval movement ($\sigma_{s=l}$) | ~uniform(0,0.25 * P)|
|Recruitment variation ($\sigma_{r}$) |  $\in\{0,0.05,.1,.2\}$|
|Recruitment autocorrelation ($ac_{r}$) |  $\in\{0,0.05,.1,.2\}$|
|DD adult movement (dmod) | $\in\{0.25,1\}$|
|Density-dependence timing | $\in\{local, global,post-dispersal\}$|
|\% Patches in MPA | ~uniform(0.01,1)|
|Initial fishing relative to natural mortality | ~uniform(0.01,4)|
|Selectivity as a multiple of maturity length| ~uniform(0.1,1.25)|
|Fleet model| $\in\{open-access, constant-effort,constant-catch\}$|
|Spatial effort model| $\in\{uniform, biomass,profits\}$|
|Years into simulation to start MPA| ~round(uniform(5,0.66 * T))|
|MPA is sprinkler?| $\in\{TRUE,FALSE\}$|
|Randomly place MPA?| $\in\{TRUE,FALSE\}$|
|Fleet reaction to MPA| $\in\{concentrate, abandon-ship\}$|
|Patchiness | ~uniform(0.01,0.75)|
|MPA habitat factor| $\in\{1, 4\}$|

```{r did-coefs, results = "asis",eval = TRUE}
did_fit %>%
  broom::tidy(intervals = TRUE, prob = 0.89) %>%
  select(term, estimate, lower, upper) %>%
  rename(
    mean = estimate,
    lower_89th_ci = lower,
    upper_89th_ci = upper
  ) %>%
  knitr::kable(
    digits = 2,
    caption = "Posterior means and credible interval for key model coefficients",
    longtable = TRUE,
    booktabs = TRUE ) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header"))

>>>>

@@

The simulation model consists of 50 patches with wrapped edges. For any one simulation we randomly pull a species and its associated life history traits from the `FishLife` [@thorson2017c] package. We pair these data with randomly selected values governing the characteristics of the simulation (Table.\@ref(tab:sim-table)). These include parameters governing recruitment (variation, autocorrelation, and timing), movement (magnitude of larval and adult dispersal and density dependent movement), fleet dynamics (degree of fishing pressure, distribution of fishing effort), and MPA design (size and placement, habitat characteristics, larval source). The population begins at unfished equilibrium. After fishing effort is applied, each simulation is run to equilibrium with and without the selected MPA design (holding all else constant). In each time step, we measure the difference in biomass densities between the scenario with and without the MPAs to calculate the population effect of the MPAs over time. Simulation results provide a library of plausible MPA effects for a range of biological and economic assumptions.

@@

where $d_i$ is the biomass density at observation *i*, *T* indicates whether the observation *i* is for a targeted ($T = 1$) or non-targeted ($T = 0$) species, and *MPA* marks whether observation *i* is in a pre MPA ($MPA = 0$) or post MPA ($MPA = 1$) state. **B^c^** is a vector of coefficients for additional control variables in matrix *X* such as water visibility and observer experience. **B^s^** is a vector of hierarchical coefficients for each sampling location **S** , clustered by island.  Under the assumptions of this model, $\beta_3$ is the causal effect of the treatment (*MPA*) on the treated (targeted species). $\beta_0$ is the mean total biomass of non-targeted species pre-MPA, and $\beta_1T$ is the mean total biomass of targeted species pre-MPA. $\beta_2MPA$ is the effect of the post-MPA period on the non-targeted species. The shape and scale parameters of the Gamma distribution are estimated as well. Regression details and diagnostic plots are available in the online appendix. The full table of covariates and their posterior means and 89% credible interval can be found in Table.\@ref(tab:coef-table).

@@

```{r sim-table, results = "asis", echo=FALSE}
variable <- c(
"Scientific Name",
"steepness",
"Adult movement ($\\sigma_{s=a}$)",
"Larval movement ($\\sigma_{s=l}$)",
"Recruitment variation ($\\sigma_{r}$)",
"Recruitment autocorrelation ($ac_{r}$)",
"DD adult movement",
"Density-dependence timing ",
"% Patches in MPA",
"Initial fishing relative to natural mortality",
"Selectivity as a multiple of maturity length",
"Fleet model",
"Spatial effort model",
"Years into simulation to start MPA",
"MPA is Larval Source?",
"Randomly place MPA?",
"Fleet reaction to MPA",
"Patchiness",
"MPA habitat factor")

distribution <- 
c(
"Drawn from all possible species in `FishLife` (@thorson2017c)",
"uniform(0.6,0.95)",
"uniform(0,0.25 * P)",
"uniform(0,0.25 * P)",
 "$\\in{0,0.05,.1,.2}$",
 "$\\in{0,0.05,.1,.2}$",
 "$\\in{0.25,1}$",
 "$\\in{Local, Global,PostDispersal}$",
 "uniform(0.01,1)",
 "uniform(0.01,4)",
 "uniform(0.1,1.25)",
"$\\in{OpenAccess, ConstantEffort,ConstantCatch}$",
 "$\\in{Uniform, Biomass,Profits}$",
 "uniform(5,0.66)",
"$\\in{TRUE,FALSE}$",
"$\\in{TRUE,FALSE}$",
"$\\in{Concentrate,Leave}$",
"uniform(0.01,0.75)",
"$\\in{1, 4}$"
)

equations <- tibble(Variable = variable, Distribution = distribution )

knitr::kable(equations,
             escape = FALSE,
             caption = "Variables for MPA simulations. U mean uniform",
             format = "pipe") %>% 
  kableExtra::kable_styling()

```{r coef-table, results = "asis", echo=FALSE}

coefs <- did_fit %>%
  broom::tidy(intervals = TRUE, prob = 0.89) %>%
  select(term, estimate, lower, upper) %>%
  rename(
    Mean = estimate,
    `Lower 89th Percentile` = lower,
    `Upper 89th Percentile` = upper
  )

  knitr::kable(
    coefs,
    digits = 2,
    caption = "Posterior means and credible interval for key model coefficients. Conditional on the assumptions of the model, the targeted:year_bins coefficients reflect the effect of the MPAs on mean total biomass of targeted finfish in the Channel Islands. targeted indicates whether the species in question is targeted, 'var' refers to a covariate, where tex = technican experience, surge is mean reported surge, kelp is mean reported kelp cover, lag catch is the total reported catch for targeted species in the previous year, temp is the mean temperature at a site, temp_dev is the deviation of a temperature observation from the mean temperatuer for that island in question",
    format = "pipe")
